API design for machine learning software: experiences from the scikit-learn project

### 2013-08-05 paper.tex
trim to get scaling example back on one page

Apart from \texttt{predict}, predictors may also implement methods
for quantifying the confidence of a prediction. In the case of
linear models, the \texttt{decision\_function} method returns
the distance of the samples to the separating hyperplane. Some
predictors also provide a \texttt{predict\_proba} method which returns
class probabilities for the input samples \texttt{X\_test}.

Finally, predictors should also provide a \texttt{score} function to assess the
performance on some input data. In supervised learning estimators, this method
takes as input arrays \texttt{X\_test} and \texttt{y\_test} and typically
computes the coefficient of determination between \texttt{y\_test} and
\texttt{predict(X\_test)} in regression, or the accuracy
in classification.
The only requirement is that the \texttt{score} method return a value
that quantifies the quality of its predictions (the higher, the better).
Unsupervised learning estimators may also expose a \texttt{score} function
to compute, for instance, the likelihood of the given data under its model.

>>>>

Apart from \texttt{predict}, predictors may also implement methods
that quantify the confidence of predictions. In the case of
linear models, the \texttt{decision\_function} method returns
the distance of samples to the separating hyperplane. Some
predictors also provide a \texttt{predict\_proba} method which returns
class probabilities.

Finally, predictors must provide a \texttt{score} function to assess their
performance on a batch of input data. In supervised estimators, this method
takes as input arrays \texttt{X\_test} and \texttt{y\_test} and typically
computes the coefficient of determination between \texttt{y\_test} and
\texttt{predict(X\_test)} in regression, or the accuracy
in classification.
The only requirement is that the \texttt{score} method return a value
that quantifies the quality of its predictions (the higher, the better).
An unsupervised estimator may also expose a \texttt{score} function
to compute, for instance, the likelihood of the given data under its model.
